Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-03-08 manuscript.Rmd
worked on intro; added renv to project

In recent years, the study of pollen grain chemistry has lead to new information important for biological and palaeoecological research.
Taxonomic differences have been identified in the chemistry of pollen, which highlight the potential of pollen identification with chemical methods in palaeoecological research.
Chemical fingerprinting of pollen has the potential of higher taxonomic resolution, automation of pollen identification and offers a more objective method than traditional morphological methods.
as well as an environmental signal stored in the chemistry of pollen (UV Proxy), which could be used as a UV-proxy.

@@

FTIR used on fossil papers in the past use acetolysed pollen or other chemically extracted pollen. 
There has not been a comparison between fresh and untreated fossil pollen.
In order to compare which compounds are missing and still present in fossil pollen.
chemical degradation of pollen during diagenesis or depth.

@@

>>>>

In recent years, the study of pollen grain chemistry has shown promising results for biological and palaeoecological research.
Fourier Transform Infrares (FTIR) spectroscopy has become a popular method for analysing pollen chemsitry
A number of FTIR studies have identified pollen chemical differences on genus level, which may extent to species level differences. 
This is a promising finding for the application of pollen identification with chemical methods in palaeoecological research, because it has the potential to increase taxomonic resolution.
Further, chemical methods are suitable for automation and offer a more objective method than traditional morphological methods.
In addition to taxonomic differences in pollen chemistry, there is evidence of environmental signals that are recorded in the chemistry of pollen.
Several studies have shown links between solar and UV radiation and pollen chemistry as well as responses in pollen chemistry to temperature changes.

So far, most FTIR studies have used modern material or material extracted from herbarium specimens.
In some cases the pollen samples are processed with acetolysis following standard palynological methods (Erdman) to simulate fossilization.
The assumption is that acetolysis does not alter the chemistry of sporopollenin and is not affecting any chemical signal.
To date, there has not been a comparison between acetolysed and untreated fossil pollen to examine any effect of acetolysis on sporopollenin or chemical degradation of pollen during diagenesis.

In this study we investigate the chemistry of fossil pollen to explore three potential sources of chemical alteration: i. the effects of diagenesis, ii. acetolysis and iii. age on pollen chemistry.
We extracted pollen from three sediment cores using density separation to obtain chemically untreated fossil spectra.
The pollen was collected from three different cores in three locations (Germany and Norway), which allows us examine potential differences in diagenesis on pollen chemistry at different locations.
One replicate of the pollen samples in each core were acetolysed to analyse any changes caused by the strong acid treatment and compared to the untreated replicate.
Each core was sub sampled at different depths to allows us to investigate chemical changes in the pollen with age.

@@

@@

Three cores from different environments and age ranges
